Using Metric Space Indexing for Complete and Efficient Record Linkage

### 2017-11-21 paper.tex
Update on Overleaf.

\textbf{Traditional  blocking:}
The additional parameters are the set of blocking keys and the
normalization encodings applied to each field. These are selected as
described in \cite{Chr12b}, exploiting knowledge of the domain and of
the records being linked, and chosen with the intention of giving the
best possible results for the datasets.
%
Each record in $A$ is placed into the appropriate block based on its
blocking key value. The algorithm then iterates over the records in $B$,
and for each one, compares it with each of the records from $A$ in the
block with the same blocking key value.

@@

% Peter 31 Oct: table style follows LNCS style guide

\begin{table}[t]
\caption{Characteristics of data sets used in the experiments.}
 \label{table-datasets}
  \centering
  \begin{scriptsize}
  %\addtolength{\tabcolsep}{-0.5pt}
  \begin{tabular}{ccccc}
  \hline\noalign{\smallskip}
  Data set~ & ~Records in~& ~Records in~ & ~Number of true~& ~Entities\\
  name(s)  & dataset1  & dataset2  & matching pairs & linked \\
  \noalign{\smallskip} \hline \noalign{\smallskip}
  CORA  & 1,295 & 1295 & 17,184 & publication-publication\\
  NCVR  & ~224,073~ & 224,061 & ~148,036~ & voter-voter\\
  Isle of Skye & 17,612 & 12,284& 2,900 & birth-death\\
  Kilmarnock  & 38,430 & 23,714 & 8,300 & birth-death\\
  \noalign{\smallskip} \hline
  \end{tabular}
  \end{scriptsize}
\end{table}

@@

The second are two randomly selected sub-sets extracted from the North Carolina Voter Registration
database (\emph{NCVR})~\footnote{Available from: \texttt{http://dl.ncsbe.gov/}}, which were collected in April and June
2014. Each of these contains records of voters including their
first names, surnames, and addresses. Ground truth is provided via a
\emph{NCID} identifier which uniquely identifies a voter.

@@

\begin{table}[t]
\caption{Parameter settings used for the different data sets used in
   the experiments,with $d$ the distance threshold used, $l_{ss}$, $l_{sb}$ and $l_{nb}$ the LSH
   shingle size, and the size and number of bands, respectively.}
 \label{table-parameters}
  \centering
  \begin{scriptsize}
  %\addtolength{\tabcolsep}{-0.5pt}
  \begin{tabular}{ccccc}
  \hline\noalign{\smallskip}
  Data set~ & $d$ & $l_{ss}$ & $l_{bs}$ & $l_{nb}$ \\
  name(s) & & & &  \\
  \noalign{\smallskip} \hline \noalign{\smallskip}
  CORA & ~$[0,5,10,\ldots,95,100]$~ & ~$2$~ &
    ~$[2,5,10]$~ & ~$[2,5,10]$~  \\
  NCVR  &  \\
  Isle of Skye &  \\
  Kilmarnock  &  \\
  \noalign{\smallskip} \hline
  \end{tabular}
  \end{scriptsize}
\end{table}

% \smallskip
% \textbf{Experimental Setup:}
% %
% We implemented all techniques described in Sect.~\ref{sec-approach}
% using Java (version 1.8.0\_144) and ran an extensive set of experiments on
% a compute server with 24 Intel(R) Xeon(R) processors running at 2.30GHz, 
% 128 GBytes of main memory and running Red Hat 4.8.5-11.

@@

discuss measures used. PC, PQ, num comparisons, time? etc.

@@

In this section, we perform linkage on the Cora data set using all four approaches presented in this paper: brute force, traditional blocking, LSH and M-Tree.
The brute-force approach is used to establish the threshold value that yields the best possible linkage for the Cora dataset. The threshold value is varied between 0 and 250, \Cref{fig-cora-quality} presents the precision, recall, and F-measure values. 
The linkage results have high precision and low recall for low threshold values, and high recall and low precision for high threshold values.
For this data set, the maximum F-measure value is achieved using a threshold value of 70. This value is data dependent; for different datasets the maximum F-measure will correspond to different thresholds. 
In the rest of this section we fix the threshold value to be 70 which maximises the F-measure for this dataset.

\begin{figure}
\begin{verbatim}
Figure 3 will be a table of Comparisons, F1, precision recall and pairs stuff.
12 ROWS ISH
\end{verbatim}
\caption{Linkage Quality using Brute Force linking on the Cora data set\label{fig-cora-quality}}
\end{figure}

\subsubsection{Traditional Blocking}

Traditionally, blocking is a method for choosing candidates for linkage using manually designed criteria.
Thanks to blocking, a distance is only computed between promising pairs of records.
A major disadvantage of traditional blocking is the need for extra engineering effort.
Bespoke blocking strategies need to be designed for a given data set and application domain.
In this section we experiment with using each key field in the Cora data set as a blocking key one by one, followed by a very permissive blocking key which takes the union of all the blocks attained by using individual key fields.

\emph{AL: The above needs more explanation and not the first bit?}

TODO: Explain pairs-quality and pairs-completeness~\Cref{cora-traditional}.

\begin{figure}
\includegraphics[width=\textwidth]{figures/plotFixedThresholdTraditional2_--_Cora_-_TradBlocking_-_70}
\caption{Blocking Quality using traditional blocking on the Cora data set\label{cora-traditional}}
\end{figure}

@@

\subsection{LSH}

LSH is a method for performing blocking without the engineering overhead of traditional blocking.
It is parameterised over two integer values: number of bands, and band sizes~\footnote{LSH can also be parameterised over the shingle size, but in this paper we set the shingle size to 2.}.

@@

\subsection{NCVR}

>>>>

\textbf{Traditional  blocking:}
The additional parameters are the set of blocking keys and the
normalization encodings applied to each field. These are selected as
described in \cite{Chr12b}, exploiting knowledge of the domain and of
the records being linked, and chosen with the intention of giving the
best possible results for the datasets.
Each record in $A$ is placed into the appropriate block based on its
blocking key value. The algorithm then iterates over the records in $B$,
and for each one, compares it with each of the records from $A$ in the
block with the same blocking key value.

\textbf{THIS TEXT WAS LIFTED FROM BELOW USE HERE? Traditionally, blocking is a method for choosing candidates for linkage using manually designed criteria.
Thanks to blocking, a distance is only computed between promising pairs of records.
A major disadvantage of traditional blocking is the need for extra engineering effort.
Bespoke blocking strategies need to be designed for a given data set and application domain.}

@@

\begin{table}[t]
\caption{Characteristics of data sets used in the experiments.}
 \label{table-datasets}
  \centering
  \begin{scriptsize}
  %\addtolength{\tabcolsep}{-0.5pt}
  \begin{tabular}{ccccc}
  \hline\noalign{\smallskip}
  Data set~ & ~Records in~& ~Records in~ & ~Number of true~& ~Entities\\
  name(s)  & dataset1  & dataset2  & matching pairs & linked \\
  \noalign{\smallskip} \hline \noalign{\smallskip}
  CORA  & 1,295 & 1295 & 17,184 & publication-publication\\
  Isle of Skye & 17,612 & 12,284& 2,900 & birth-death\\
  Kilmarnock  & 38,430 & 23,714 & 8,300 & birth-death\\
  \noalign{\smallskip} \hline
  \end{tabular}
  \end{scriptsize}
\end{table}

@@

@@

\begin{table}[t]
\caption{Parameter settings used for the different data sets used in
   the experiments,with $d$ the distance threshold used, $l_{ss}$, $l_{sb}$ and $l_{nb}$ the LSH
   shingle size, and the size and number of bands, respectively.}
 \label{table-parameters}
  \centering
  \begin{scriptsize}
  %\addtolength{\tabcolsep}{-0.5pt}
  \begin{tabular}{ccccc}
  \hline\noalign{\smallskip}
  Data set~ & $d$ & $l_{ss}$ & $l_{bs}$ & $l_{nb}$ \\
  name(s) & & & &  \\
  \noalign{\smallskip} \hline \noalign{\smallskip}
  CORA & ~$[0,5,10,\ldots,95,100]$~ & ~$2$~ &
    ~$[2,5,10]$~ & ~$[2,5,10]$~  \\
  Isle of Skye &  \\
  Kilmarnock  &  \\
  \noalign{\smallskip} \hline
  \end{tabular}
  \end{scriptsize}
\end{table}

% \textbf{Experimental Setup:}
% %
% We implemented all techniques described in Sect.~\ref{sec-approach}
% using Java (version 1.8.0\_144) and ran an extensive set of experiments on
% a compute server with 24 Intel(R) Xeon(R) processors running at 2.30GHz, 
% 128 GBytes of main memory and running Red Hat 4.8.5-11.

@@

@@

In this section, we perform linkage on the Cora data set using all four approaches presented in this paper: brute force, traditional blocking, LSH and M-Tree.
The brute-force approach is used to establish the threshold value that yields the best possible linkage for the Cora dataset. The threshold value is varied between 0 and 250, \Cref{fig-cora-brute} presents the precision, recall, and F-measure values. 
The linkage results have high precision and low recall for low threshold values, and high recall and low precision for high threshold values.
For this data set, the maximum F-measure value is achieved using a threshold value of 70. This value is data dependent; for different datasets the maximum F-measure will correspond to different thresholds. 
In the rest of this section we fix the threshold value to be 70 which maximises the F-measure for this dataset.

\begin{figure}
\includegraphics[width=\textwidth]{figures/plotLQ_--_Cora_-_Brute_Force.png}
\caption{Linkage Quality using Brute Force linking on the Cora data set\label{fig-cora-brute}}
\end{figure}

In the traditional blocking experiment the following fields from the Cora data set are used as a blocking key: \textit{author}, \textit{title}, \textit{venue}, \textit{location}, \textit{publisher} and \textit{year}. We also use a very permissive blocking key which takes the union of all the values for these fields.

\Cref{comparison-of-results} shows the results of the Cora experiments. The table shows the parameters for the experiment, the number of distance comparisons made, the precision, recall and F1 measure and the pairs quality and pair completeness achieved by each algorithm.

TODO: Explain pairs-quality and pairs-completeness.
\emph{\textbf{TODO: discuss measures used. PC, PQ, num comparisons, time? etc.}}

\begin{figure}
\begin{verbatim}
Figure 3 will be a table of Comparisons, F1, precision recall and pairs stuff.
12 ROWS ISH
\end{verbatim}
\caption{Linkage Quality using Brute Force linking on the Cora data set\label{comparison-of-results}}
\end{figure}

@@

@@
